25 years of Social Work Research

### 2015-02-11 dataCleaning.Rmd
General update.

---
title: "History of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: pdf_document
---

@@

full.df$record <- ifelse(full.df$record == 
        "Journal of Sociology & Social Welfare",    # Spelling difference
        "Journal of Sociology and Social Welfare",  
                        full.df$record)
```

@@

```{r}
years <- c("2014", "2015")
ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

+ Journal titles that did not have any clear publication history (e.g., due to an indexing error).  This exclusion was based on errors in data entry.

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Multicultural Social Work",
    "Journal of Social Work Process",
    "Journal of Teaching in Social Work", 
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
        "The British Journal of Pyschiatric Social Work",       # Old title
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

full.df$record <- ifelse(full.df$record == "Journal of Independent Social Work" | full.df$record == "Journal of Analytic Social Work", "Psychoanalytic Social Work", 
                full.df$record)

# Journals were originally merged after suffixes were eliminated (after the colon).  Thus, Practice: Social Work in Action  (new title) was shortened to Practice (old title).  This section resolves two of these issues to be consistent in the comparison with Hodge.

@@

# Coverage via Hodge article

```{r hodgeCompare, eval=FALSE}
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)

```

@@

+ to do ... summary with hodge list

@@

This section examines the overall _coverage_ of the current search by making systematic comparisons with Hodge (2013).  The first analysis shows how the list of SWH overlaps with HL -- that is, the journals that were common to both lists (_intersection_).  The sedond analyses shows the set _differences_.  The third analysis focuses on the union of the sets.  The union shows a meta-list by 
```{r}

@@

hodge.swHistory.union <- union(hodge, unique.swHistory$record)

print(sort(hodge.swHistory.intersect))
print(sort(hodge.swHistory.diff))
print(sort(swHistory.hodge.diff))
print(sort(hodge.swHistory.union))

```

@@

Reflections: Narratives of Professional Helping

>>>>

---
title: "25 years of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: pdf_document
---

@@

full.df$record <- ifelse(full.df$record == 
        "Journal of Sociology & Social Welfare",    # Spelling difference
        "Journal of Sociology and Social Welfare",  
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)
```

@@

```{r}

year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

+ Journal titles that did not have any clear publication history based on a broad-based Internet search and other databases (e.g., ProQuest).  These exclusions are assumed to be data entry problems at time of indexing.

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Social Work Process",
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
    "The British Journal of Pyschiatric Social Work", # Old
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

full.df$record <- ifelse(full.df$record == 
        "Journal of Independent Social Work" | full.df$record ==    # New title
        "Journal of Analytic Social Work",                          # Old title
        "Psychoanalytic Social Work",                               # Old title
                full.df$record)

# Journals were originally merged after suffixes were eliminated (after the
# colon).  Thus, Practice: Social Work in Action  (new title) was shortened to
# Practice (old title).  This section resolves two of these issues to be
# consistent in the comparison with Hodge.

@@

@@

## Revised database

This section provides a summary of the revised database after the initial processing with the `ebscoBWR` function and the subsequent data cleaning.  An additional code is included in this summary to indicate whether the journal title overlaps with the list of Hodge (indicated by *H*).

@@

This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, _differences_, and _union_ of the lists.
```{r}
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

hodge.swHistory.union <- union(hodge, unique.swHistory$record)
```

This list shows which journal titles are common to both lists.

```{r}
print(sort(hodge.swHistory.intersect))
```

This list shows the articles on Hodge but not the current study.

```{r}
sink(file = "JournalsMissed.txt")
print(sort(hodge.swHistory.diff))
sink()
```
This list shows the articles on the current study but not on Hodge.

```{r}
print(sort(swHistory.hodge.diff))
```

This list shows the union of lists -- that is, a full list of all titles by combining a list.  It would be useful to break out the former titles of journals, as well as the years of existence.  This would establish a complete listing of all social work journals, both current and historical.

```{r}
print(sort(hodge.swHistory.union))
```

## Descriptive summary of records

```{r comment=NA, echo=TRUE} 
number.of.articles <- length(which(full.df$attributes == "article"))
range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
```

@@

```{r}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

ggplot(cor.data, aes(x = no.years, y = n)) + 
            geom_point(shape = 1) + 
            geom_smooth() + 
            xlab("Years") + 
            ylab("Number of articles")

cor(cor.data$no.years, cor.data$n)
```
